% =============================================================================
% Freelance experience — three separate position entries (LTCA / KGW / EC)
% Use: copy into resume_main.tex after \begin{adjustwidth}{2em}{0em} in Experience.
% =============================================================================

\positionAndCompanyLine{Fullstack developer}{freelance; project: Akademia LTCA}{10/2024 - now}
\project{Akademia LTCA}{Cross-platform learning app (web + iOS/Android via Capacitor); solo ownership.}
\begin{flushleft}{\badge{lavenderBlue}{Responsibilities}}\end{flushleft}
\begin{itemize}
    \item Full-stack front-end: architecture and stack (React, TypeScript, Vite, TanStack, Tailwind, Radix), API layer (axios, auth, 401 handling), file-based routing.
    \item PWA + Capacitor: single codebase for web and native, Workbox caching, offline strategy, platform builds (dev/staging/prod).
    \item Auth (token validation, proactive logout), offline detection, error monitoring and Sentry, push (OneSignal), live updates (Capawesome), i18n (PL).
    \item Quality: Vitest, Playwright, Storybook, ESLint, Prettier, Husky, conventional commits; internal docs for onboarding.
    \item CI/CD: Azure Pipelines, multi-environment builds, Capacitor sync and store builds.
\end{itemize}
\techStackList{React, TypeScript, Vite, TanStack Router/Query/Table, Zustand, Tailwind, Radix UI, Capacitor, Workbox, Vitest, Playwright, Azure Pipelines; backend: Node.js/Express, Pino, PM2, Docker.}
\vspace{0.5em}

\positionAndCompanyLine{Fullstack developer}{freelance; project: KGW}{12/2025 - now}
\project{KGW}{Association management platform — meetings, protocols, resolutions, tasks; team of 2.}
\begin{flushleft}{\badge{lavenderBlue}{Responsibilities}}\end{flushleft}
\begin{itemize}
    \item Implemented Tasks (feature, comments, 2-column list grid); extended Meetings (sorting, grid, protocol/resolution flow, mobile).
    \item Protocols \& Resolutions: protocols–meetings integration (Epic 54), sortable lists, print/signatures, status and permissions.
    \item Members \& permissions: secretary positions, member access to protocols/resolutions/meetings; sliding-window auth.
    \item UI/UX: modals, list redesign, mobile views; PR-based workflow.
\end{itemize}
\techStackList{Nuxt 4, Vue, Quasar, TypeScript, Pinia.}
\vspace{0.5em}

\positionAndCompanyLine{Cloud Engineer}{LetzCode (External service provider to the European Commission)}{03/2025 - 05/2025}
\project{Network management}{Migration of NSX-T network settings to Terraform.}
\techStackList{NSX-T, Terraform, Python.}
\vspace{0.5em}
